### 2016-07-09 version0.0/asli.tex
finishing intro

\newcommand\acknowlege[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Acknowledgements\normalsize\\\indent\\#1\newpage
  \fi
}
\newcommand\dedications[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Dedication\normalsize\\\indent\\#1\newpage
  \fi
}
%\renewcommand{\appendixtocname}{\Huge \textbf{List of Appendices} \normalsize}
\newcommand{\blank}{\hspace{-2mm}}
\newcommand{\super}{Dr. P. M. Barmby} %supervisor
\newcommand{\sco}{Dr. E. Peeters}  %member of supervisory committee
\newcommand{\sct}{Dr. G. Osinski}  %other member of supervisory committee (lbin)
\newcommand{\examo}{Dr. R. Abraham}  %examining committee (up to four, if less leave blank)
\newcommand{\examt}{Dr. M. Daley}
\newcommand{\examth}{Dr. S. C. Gallagher}
\newcommand{\examf}{Dr. P. Wiegert}
\newcommand{\department}{Physics and Astronomy}
\newcommand{\degree}{Doctor of Philosophy}
\newcommand{\firstname}{Sahar}
\newcommand{\middlename}{}
\newcommand{\lastname}{Rahmani}
%\renewcommand{\author}[1]{\ifx\empty#1\else\gdef\@author{#1}\fi} 
\newcommand{\authorname}{{\firstname} {\middlename} {\lastname}}
\newcommand{\titl}{What governs star formation in galaxies? A modern statistical approach}
\newcommand{\spinetitle}{Extragalactic star formation}%only if the above is more than 60 characters
\newcommand{\thesisformat}{Integrated Article} %or Integrated Article
\newcommand{\gyear}{\number\year}
\newcommand{\makecoauthor}{
%Type information about coauthorship here/
Thanks to Sophia, Hossein and Els. 
}
\newcommand{\makeacknowlege} {
I would like to thank all my Friends in Western. Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam, Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad,
}
\newcommand{\makededications} {
To my parents, my sisters, and Matin, for their unconditional love and support. 
}
\newcommand{\listappendixname}{List of Appendices}
\newlistof{myappendices}{app}{\listappendixname}
\newcommand{\myappendices}[1]{%
\addcontentsline{app}{myappendices}{#1}\par}

@@

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $\ }
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand \sii {S~{\textsc II}} 
\newcommand \oiii {O~{\textsc III}} 
\newcommand \hi {H~{\textsc I}\ }
\newcommand \hii {H~{\textsc II}\ }
\newcommand \oii {O~{\textsc II}}

>>>>

\newcommand\acknowlege[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Acknowledgements\normalsize\\\indent\\#1\newpage
  \fi
}
\newcommand\dedications[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Dedication\normalsize\\\indent\\#1\newpage
  \fi
}
%\renewcommand{\appendixtocname}{\Huge \textbf{List of Appendices} \normalsize}
\newcommand{\blank}{\hspace{-2mm}}
\newcommand{\super}{Dr. P. M. Barmby} %supervisor
\newcommand{\sco}{Dr. E. Peeters}  %member of supervisory committee
\newcommand{\sct}{Dr. G. Osinski}  %other member of supervisory committee (lbin)
\newcommand{\examo}{Dr. R. Abraham}  %examining committee (up to four, if less leave blank)
\newcommand{\examt}{Dr. M. Daley}
\newcommand{\examth}{Dr. S. C. Gallagher}
\newcommand{\examf}{Dr. P. Wiegert}
\newcommand{\department}{Physics and Astronomy}
\newcommand{\degree}{Doctor of Philosophy}
\newcommand{\firstname}{Sahar}
\newcommand{\middlename}{}
\newcommand{\lastname}{Rahmani}
%\renewcommand{\author}[1]{\ifx\empty#1\else\gdef\@author{#1}\fi} 
\newcommand{\authorname}{{\firstname} {\middlename} {\lastname}}
\newcommand{\titl}{What governs star formation in galaxies? A modern statistical approach}
\newcommand{\spinetitle}{Extragalactic star formation}%only if the above is more than 60 characters
\newcommand{\thesisformat}{Integrated Article} %or Integrated Article
\newcommand{\gyear}{\number\year}
\newcommand{\makecoauthor}{
%Type information about coauthorship here/
Thanks to Sophia, Hossein and Els. 
}
\newcommand{\makeacknowlege} { 1) Pauline
2) Els, Sophia, Hossein,
3)I would like to thank all my Friends in Western. Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam, Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
4) bacheha
5) western ppl; Jodi, Brian, Henry, Phin,...
6) Mohad, shahin, pejman, pouria, masood,babak
7) fako famil
}
\newcommand{\makededications} {
To my parents, my sisters, and Matin, for their unconditional love and support. 
}
\newcommand{\listappendixname}{List of Appendices}
\newlistof{myappendices}{app}{\listappendixname}
\newcommand{\myappendices}[1]{%
\addcontentsline{app}{myappendices}{#1}\par}

@@

\newcommand \kpc {\,{\rm kpc}}
\newcommand \sigmagas {$\Sigma_{\mathrm {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\mathrm {total\, gas }} $\ }
\newcommand \eqsigmagas {\Sigma_{\mathrm {gas }}}
\newcommand \sigmasfr {$\Sigma_{\mathrm {SFR }} $\ }
\newcommand \eqsigmasfr {\Sigma_{\mathrm {SFR }}}
\newcommand \sigmastar {$\Sigma_{\mathrm {star }} $\ }
\newcommand \eqsigmastar {\Sigma_{\mathrm {star }}}
\newcommand \halpha {H$\alpha $\ }
\newcommand \um {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand \sii {[S~{\textsc II}]} 
\newcommand \oiii {[O~{\textsc III}]} 
\newcommand \hi {H~{\textsc I}}
\newcommand \hii {H~{\textsc II}}
\newcommand \oii {[O~{\textsc II}]}
\newcommand \nii {[N~{\textsc II}]}
